% !TeX root = ../thuthesis-caishiyu.tex

% 中英文摘要和关键字

\begin{abstract}
    传统的数据库采用内存-非易失性介质的双层架构。
    数据库的数据有两份拷贝，一份拷贝存储在内存中以提高事务访问的性能，另一份拷贝存储在非易失性介质上以保证数据持久化。
    传统数据库需要频繁地将数据从内存同步到非易失性介质上，并且使用日志、检查点等机制保证数据的更新不会丢失。这些数据同步和数据管理的开销显著影响了数据库的性能。

    非易失性内存（Non-Volatile Memory, NVM）是一种新的存储介质。
    NVM 支持字节寻址以及数据非易失性，同时其访问延迟与 DRAM 处于同一个数量级。
    NVM 硬件的出现给数据库研究提供了新的方向，即设计单层存储架构的数据库。
    单层架构的数据库将所有数据存储在 NVM 上，其允许事务低延迟地访问和更新 NVM 上的数据，进而能够减少数据同步的开销，并使系统运行无日志化。

    然而无日志的前提给数据库的垃圾回收机制以及数据恢复机制带来了挑战。
    垃圾回收需要回收未被使用的空间。
    然而在无日志的前提下，数据管理无法保证分配空间以及使用空间的原子性，会造成持久化的内存泄漏问题。
    另一方面，数据库管理系统需要保证事务的原子性以及持久化，
    而日志文件记录了事务的操作。因此在恢复阶段，系统难以在无日志的前提下消除未提交事务的造成的片面影响。

    基于现有 NVM 工作的设计思路，本文设计了不基于日志系统的垃圾回收机制以及数据恢复机制。
    本文的主要贡献如下：
    \begin{enumerate}
        \item 本文采用了事务粒度的垃圾回收机制。在系统运行时，垃圾回收机制会尽可能地回收事务产生的不可见的数据结构，以提高 NVM 存储空间的利用率。在恢复阶段，垃圾回收机制会回收泄漏的存储空间。
        \item 本文了结合了无日志的 NVM 分配器的设计思路，设计出第一个不基于日志的数据库恢复机制。本文通过设计 NVM 上数据结构来保证数据恢复时 NVM 数据的可读性。通过设计关键数据结构的可见性判断，系统能够在保证数据库 ACID 特性的前提下花费较低开销恢复到正常工作状态。
        \item 真实环境下的实验表明，垃圾回收机制能够在至多降低 $10\%$ 的性能的前提下，帮助系统节约至多 $67\%$ 的存储空间。与基于预写日志 InnoDB 的恢复性能对比实验表明，无日志的数据恢复机制的恢复时间比 InnoDB 的恢复时间低至多三个数量级。并且该数据恢复机制仅需要 InnoDB 一半的存储空间。
    \end{enumerate}

    % 关键词用“英文逗号”分隔，输出时会自动处理为正确的分隔符
    \thusetup{
        keywords = {非易失性内存, 数据库管理系统, 垃圾回收, 数据恢复, 日志},
    }
\end{abstract}

\begin{abstract*}
    Traditional database management system (DBMS) uses a two-layer storage architecture.
    There are two copies of the record data, one in memory as a high-speed buffer and one in non-volatile storage to ensure data durability.
    The data synchronization overhead between the two storage and the complexity of data management are the bottlenecks of traditional databases.

    Non-volatile memory (NVM) supports byte-addressable memory access which is similar to DRAM, while at the same time, NVM can keep the
    in-memory data persistent like disks.
    The commercialization of NVM has provided a new direction for database research, namely the adoption of single-layer storage architecture.
    A single-layer architecture for database management systems can reduce the overhead of data synchronization and make the system run without logging.

    However, the log-freedom property poses a challenge to garbage collection  and data recovery of DBMS.
    With no logs, data management cannot guarantee the atomicity of memory allocation, which can lead to memory leaks.
    The memory leaks on NVM are persistent and are harmful to DBMS.
    On the other hand, the DBMS needs to ensure the atomicity and durability of transactions during the data recovery phase.
    The log file records the operation of the transaction. Thus, it is difficult for the system to eliminate the partial effects of uncommitted transactions without logging.

    Based on the design choices of existing NVM works, this paper presents garbage collection and data recovery for a log-freedom NVM-based DBMS.
    The main contributions of this paper are as follow:

    \begin{enumerate}
        \item This paper presents a transaction-level garbage collection that enables the DBMS to reclaim invisible data structures as soon as possible and saves NVM space. In the data recovery phase, the garbage collection reclaims the storage space to avoid potential memory leaks.
        \item This paper presents the first log-freedom data recovery mechanism which is based on the design choice of log-freedom NVM allocator. This paper ensures the readability of NVM data after reboot by designing the data structure on NVM. This paper also proposes visibility rules for key data structures. The rules enable the system to go back to work with less overhead while ensuring ACID properties.
        \item  This paper evaluates garbage collection and data recovery on Intel Optane DC PMM. The evaluation shows that enabling garbage collection results in up to
              10\% performance degradation, but saves up to 67\% storage space. Besides, our data recovery requires only 0.2\%
              of the time and half of the storage space of InnoDB.

    \end{enumerate}


    % Use comma as seperator when inputting
    \thusetup{
        keywords* = {Non-volatile memory, database management system, garbage collection, data recovery, log},
    }
\end{abstract*}
